Re-fit

### 2022-07-12 scripts/r/04_refit/refit_sc.Rmd
♻️ - update sc refit

@@

```{r}
petauroides_fistulator_1_f0_cat <- bam(
  pitch_st ~
    effect_cat +
    s(id) +
    s(trial, bs = "re") +
    s(speaker, bs = "re") +
    s(target_name, bs = "re") +
    s(target_colour, bs = "re") +
    s(competitor_name, bs = "re") +
    s(competitor_colour, bs = "re") +
    s(distractor1_name, bs = "re") +
    s(distractor1_colour, bs = "re") +
    s(distractor2_name, bs = "re") +
    s(distractor2_colour, bs = "re"),
  data = msa_data,
  cluster = parallel::makeCluster(8)
)

saveRDS(petauroides_fistulator_1_f0_cat, "./data/analyses/models/petauroides_fistulator_1_f0_cat.rds")
```

@@

>>>>

# nestor_idahoensis

```{r}
msa_data <- read_csv("./data/analyses/sc/nestor_idahoensis/msa_data_v2.csv", na = c("", "--undefined--")) %>%
  mutate(
    effect_cat = factor(typicality, levels = c("atypical", "medium", "typical")),
    f0 = scale(log(f0)) %>% as.numeric(),
    duration = scale(log(duration)) %>% as.numeric(),
    f15 = scale(log(f15)) %>% as.numeric(),
    f25 = scale(log(f25)) %>% as.numeric()
  )
```

Not sure which priors to use after scaling.

```{r}
priors2 = c(
  #weakly informative priors for intercepts and beta for each response variable
  prior(normal(0,1.5), class = Intercept, resp = f0),
  prior(normal(0,1.5), class = b, resp = f0),
  prior(normal(0,1.5), class = Intercept, resp = duration),
  prior(normal(0,1.5), class = b, resp = duration),
  prior(normal(0,1.5), class = Intercept, resp = f15),
  prior(normal(0,1), class = b, resp = f15),
  prior(normal(0,1), class = Intercept, resp = f25),
  prior(normal(0,1), class = b, resp = f25),
  #weakly informative priors for random effects (slopes)
  prior(cauchy(0,0.1), class = sd, group = ID, resp = f0),
  prior(cauchy(0,0.1), class = sd, group = ID, resp = duration),
  prior(cauchy(0,0.1), class = sd, group = ID, resp = f15),
  prior(cauchy(0,0.1), class = sd, group = ID, resp = f25),
  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f0),
  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = duration),
  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f15),
  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f25),
  #weakly informative priors for the correlation between random intercept and slope
  prior(lkj(2), class = cor, group = ID),
  prior(lkj(2), class = cor, group = targetWord),
  prior(cauchy(0, 1), class = sigma, resp=f0),
  prior(cauchy(0, 1), class = sigma, resp=duration),
  prior(cauchy(0, 1), class = sigma, resp=f15),
  prior(cauchy(0, 1), class = sigma, resp=f25)
)

nestor_idahoensis_1_mult_cat <- brm(
  mvbind(f0, duration, f15, f25) ~
    effect_cat +
    (1|ID) + (1|targetWord) +
    (0 + typicality|ID) +
    (0 + typicality|targetWord),
  data = msa_data,
  family = gaussian(),
  prior = priors2, chains = 4, cores = 4,
  threads = threading(2, grainsize = 100),
  backend = "cmdstanr",
  # control = list(max_treedepth = 15, adapt_delta = 0.9),
  file = "./data/analyses/models/nestor_idahoensis_1_mult_cat.rds",
  seed = my_seed
)
```

@@

```{r}
the_file <- "./data/analyses/models/petauroides_fistulator_1_f0_cat.rds"

if (file.exists(the_file)) {
  petauroides_fistulator_1_f0_cat <- readRDS(the_file)
} else {
  petauroides_fistulator_1_f0_cat <- bam(
    pitch_st ~
      effect_cat +
      s(id) +
      s(trial, bs = "re") +
      s(speaker, bs = "re") +
      s(target_name, bs = "re") +
      s(target_colour, bs = "re") +
      s(competitor_name, bs = "re") +
      s(competitor_colour, bs = "re") +
      s(distractor1_name, bs = "re") +
      s(distractor1_colour, bs = "re") +
      s(distractor2_name, bs = "re") +
      s(distractor2_colour, bs = "re"),
    data = msa_data,
    cluster = parallel::makeCluster(8)
  )
  saveRDS(petauroides_fistulator_1_f0_cat, the_file)
}
```

@@

# sphyrna_ellioti

```{r}
pro_df <- read.csv("data/analyses/sc/sphyrna_ellioti/Data & Analysis Files/ManySpeech_ProsodyTrialsData.csv")

#Some intervals are blank, so delete those:

pro_df <- pro_df[!pro_df$AFI=="",]

#Create a column that specifies the part of speech of the phrase of interest:

pro_df <- pro_df %>%
  mutate(POS = case_when(
    n.interval == "10" ~ "Adj",
    n.interval == "11" ~ "Noun"
  ))

#Convert continuous variables from character type to numeric:

pro_df$Duration..ms.<- as.numeric(pro_df$Duration..ms.)
pro_df$Intensity <- as.numeric(pro_df$Intensity)
pro_df$fo1 <- as.numeric(pro_df$fo1)
pro_df$fo2 <- as.numeric(pro_df$fo2)
pro_df$fo3.Hz. <- as.numeric(pro_df$fo3.Hz.)

#Centering F0 values by speaker:

pro_df <- pro_df %>%
  group_by(speaker) %>% 
  mutate(mfo1 = mean(fo1),
         mfo2 = mean(fo2),
         mfo3 = mean(fo3.Hz.),
         cfo1 = fo1-mfo1,
         cfo2 = fo2-mfo2,
         cfo3 = fo3.Hz.-mfo3)

#For now, let's just look at the critical Adjectives and Nouns:

phrase_df <- pro_df %>% drop_na(POS)

#Filling out the typicality columns for the AF and ANF conditions from the typicality mean scores
#based on the thresholds provided by the experimenters:

msa_data <- phrase_df %>%
  mutate(typicality = case_when(
    typ_mean < 25 ~ "atypical",
    typ_mean > 25 & typ_mean < 90 ~ "medium",
    typ_mean > 90 ~ "typical"
  ))

msa_data$POS <- as.factor(phrase_df$POS)
msa_data$typicality <- as.factor(phrase_df$typicality)
msa_data$condition <- as.factor(phrase_df$condition)
msa_data$AFI <- as.factor(phrase_df$AFI)

msa_data <- msa_data %>%
  mutate(
    eff_cont = scale(typ_mean) %>% as.numeric(),
    duration = log(Duration..ms.) %>% scale() %>% as.numeric(),
    intensity = scale(Intensity) %>% as.numeric(),
    cfo1 = scale(cfo1) %>% as.numeric(),
    cfo2 = scale(cfo2) %>% as.numeric(),
    cfo3 = scale(cfo3) %>% as.numeric()
  )

contrasts(msa_data$POS) <- "contr.sum"
contrasts(msa_data$condition) <- "contr.sum"
```

```{r}
sphyrna_ellioti_dur_cat <- brm(
  duration ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_dur_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)

sphyrna_ellioti_int_cat <- brm(
  intensity ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_int_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)

sphyrna_ellioti_cfo1_cat <- brm(
  cfo1 ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_cfo1_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)

sphyrna_ellioti_cfo2_cat <- brm(
  cfo2 ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_cfo2_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)
sphyrna_ellioti_cf03_cat <- brm(
  cfo3 ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_cf03_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)
```
